Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-13 paper.tex
Clarification about dynamic stall regime

The wake of a cross-flow turbine in dynamic stall has been studied via laser
Doppler velocimetry by Brochier et al. \cite{Brochier1986} and with particle
image velocimetry (PIV) by Fujisawa and Shibuya \cite{Fujisawa2001}. However,
both of these studies were performed at very low Reynolds numbers---$Re_D =
10^4$ and $10^3$, respectively. Tescione et al. \cite{Tescione2014} studied the
wake of a vertical-axis wind turbine in a wind tunnel using stereo PIV at an
approximate blade chord Reynolds number $Re_c = 1.7 \times 10^5$; very close to
the $Re$-independent state reported in \cite{Bachant2014}.

>>>>

The wake of a cross-flow turbine in the dynamic stall regime has been studied
via laser Doppler velocimetry by Brochier et al. \cite{Brochier1986} and with
particle image velocimetry (PIV) by Fujisawa and Shibuya \cite{Fujisawa2001}.
However, both of these studies were performed at very low Reynolds
numbers---$Re_D = 10^4$ and $10^3$, respectively. Tescione et al.
\cite{Tescione2014} studied the wake of a vertical-axis wind turbine in a wind
tunnel using stereo PIV at an approximate blade chord Reynolds number $Re_c =
1.7 \times 10^5$; very close to the $Re$-independent state reported in
\cite{Bachant2014}.
